Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-10 eswc-2012/phdsymp.tex
experimental design
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@54 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics relative to their own
expected application. Another possibility that opens is to better
answer the question ``what is the best general-purpose triple
store?''. I.e. can we collapse all the metrics into a single
\emph{test statistic} that can summarize the performance of the engine
as a whole? Also, can we provide a system to developers that they can
use to see if any changes they do to the engine has unexpected adverse
effects on other parts of the system?

The above relies on that the test data and queries are in fact
representative of the system as a whole, but this is usually not proven.
In physical science and engineering, conventional wisdom
has been that you should only vary one variable at a time to study the
effects of that one variable. In medical science, this has been
abandoned several decades ago, thanks to advances in statistics. In
e.g. a case where the researcher administrates different treatments to
terminally ill patients, some of which may be painful or shorten their
lives, experimental economy is extremely important.

Using techniques from statistical experimental design, I conjecture
that it is possible to design an experiment (i.e. a benchmark) so
that it provably representative of all realistic situations. This
would permit us to make rather categorical statements regarding
overall query engine performance.
